Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-05 src/paper.tex
update

\subsection{Baseline models}
All models are reflected in Table \ref{main_exp}. 
TSELM is compared with Spex+, a discriminative separation model \cite{spex_plus} trained on Libri2Mix \cite{librimix}. Since the discretization might lose some 
speaker information compared with continuous methods. We compare the speaker 
similarity of TSELM with the target audio produced by discretizating the clean audio, which is denoted by Target-discrete-WavLM.

>>>>

\subsection{Baseline models}
All models are reflected in Table \ref{main_exp}. 
TSELM is compared with Spex+, a discriminative separation model \cite{spex_plus} trained on Libri2Mix \cite{librimix}. Since the discretization might lose some 
speaker information compared with continuous methods. We compare the speaker 
similarity of TSELM with the target audio produced by discretizing the clean audio, which is denoted by Target-discrete-WavLM.
